Pricing Patterns in Organic Markets

### 2024-12-04 other/datasheet/datasheet_ Hammer.qmd
Update paper and datesheet
Fixed typo

---
title: "Datasheets for Datasets: Enhancing Transparency and Accountability in Data Collection '"
subtitle: "A Comprehensive Examination of the Project Hammer Grocery Dataset"
author: 
  - Dingshuo Li
thanks: "Code and data are available at: https://github.com/dawsonlll/Organic-Product-Pricing-Analysis.git"
date: today
date-format: long
abstract: "This datasheet documents the Project Hammer Grocery Dataset, a comprehensive compilation of historical grocery prices from Canadian retailers, with a focus on organic products. The dataset was created to address gaps in publicly available structured data, enabling the analysis of price trends, vendor strategies, and seasonal variations. By capturing detailed pricing information across vendors and regions, the dataset provides insights into market dynamics and competitive behavior in Canada’s grocery sector. This resource is critical for fostering transparency, informing policy decisions, and supporting research on consumer economics and anti-competitive practices."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Datasheets for Datasets: Enhancing Transparency and Accountability in Data Collection"
subtitle: "A Comprehensive Examination of the Project Hammer Grocery Dataset"
author: 
  - Dingshuo Li
thanks: "Code and data are available at: https://github.com/dawsonlll/Organic-Product-Pricing-Analysis.git"
date: today
date-format: long
abstract: "This datasheet documents the Project Hammer Grocery Dataset, a comprehensive compilation of historical grocery prices from Canadian retailers, with a focus on organic products. The dataset was created to address gaps in publicly available structured data, enabling the analysis of price trends, vendor strategies, and seasonal variations. By capturing detailed pricing information across vendors and regions, the dataset provides insights into market dynamics and competitive behavior in Canada’s grocery sector. This resource is critical for fostering transparency, informing policy decisions, and supporting research on consumer economics and anti-competitive practices."
format: pdf
number-sections: true
bibliography: references.bib
---

### 2024-12-04 paper/paper.qmd
Update paper and datesheet
Fixed typo

All data analysis was conducted using R @citeR, including statistical computing and graphics. And the following R packages were used for conduct code in scripts: tidyverse @tidy, Palmerpenguins @palmerpenguins, ggplot2 @ggplot2, Dplyr @citedplyr, Knitr @citeknitr, modelsummary @modelsummary, arrow @arrow, here @here, rstanarm @rstanarm, sclaes @scales, splines @splines,broom @broom, lubridate @date, janitor @jan and testthat @testthat. Following  @tellingstories we conducted data simulate, test simulated data, data cleanning, test analysis data, EDA, data modelling. The R code in scripts were adapted from @alexander2023telling

>>>>

All data analysis was conducted using R @citeR, including statistical computing and graphics. And the following R packages were used for conduct code in scripts: tidyverse @tidy, Palmerpenguins @palmerpenguins, ggplot2 @ggplot2, Dplyr @citedplyr, Knitr @citeknitr, modelsummary @modelsummary, arrow @arrow, here @here, rstanarm @rstanarm, sclaes @scales, splines @splines,broom @broom, lubridate @date, janitor @jan, stringr @stringr and testthat @testthat. Following  @tellingstories we conducted data simulate, test simulated data, data cleanning, test analysis data, EDA, data modelling. The R code in scripts were adapted from @alexander2023telling
